paper2_resistance_mechanisms_mixtures

### 2016-12-15 inst/documents/paper2/paper2_resistance_mechanisms_mixtures.Rmd
add effectiveness fig, tweak label sizes

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('exposure: 0.5', line= -2, side=2, cex=0.8) #side=1b,2l,3t,4r

@@

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), xlabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 120 )

@@

#effectiveness1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, xlabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 120 )

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('exposure: 0.8', line= -2, side=2, cex=0.8) #side=1b,2l,3t,4r

@@

#exposure 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.8 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), cex.axis = 0.6, addLegend=FALSE, main='', maxX = 120 )

@@

#eff1 & expos 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.8 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 120 )

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1: 0.5', line= -2, side=1, cex=0.8) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1: 0.8', line= -2, side=1, cex=0.8) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('dominance1: 0.5', line= -2, side=2, cex=0.8) #side=1b,2l,3t,4r

@@

#rr1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.8 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, xlabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 120 )

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('dominance1: 0.8', line= -2, side=2, cex=0.8) #side=1b,2l,3t,4r

@@

#dominance1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.8 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), cex.axis = 0.6, addLegend=FALSE, main='', maxX = 120 )

@@

#dom1 & rr1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.8 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.8 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 120 )

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('resistance restoration1: 0.5', line= -2, side=1, cex=0.8) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('resistance restoration1: 0.8', line= -2, side=1, cex=0.8) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('frequency1: 1%', line= -2, side=2, cex=0.8) #side=1b,2l,3t,4r

@@

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), xlabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 150 )

@@

#eff1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, xlabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 150 )

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('frequency1: 0.1%', line= -2, side=2, cex=0.8) #side=1b,2l,3t,4r

@@

#freq1 0.001
runcurtis_f2( max_gen=500,  P_1 = 0.001 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), cex.axis = 0.6, addLegend=FALSE, main='', maxX = 150 )

@@

#freq1 0.001, eff1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.001 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 150 )

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1: 0.5', line= -2, side=1, cex=0.8) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1: 0.8', line= -2, side=1, cex=0.8) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('male exposure: 0.8', line= -2, side=2, cex=0.8) #side=1b,2l,3t,4r

@@

runcurtis_f2( male_exposure_prop=0.8, max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), xlabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 200 )

@@

#eff1 0.8
runcurtis_f2( male_exposure_prop=0.8, max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, xlabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 200 )

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('male exposure:0.2', line= -2, side=2, cex=0.8) #side=1b,2l,3t,4r

@@

#freq1 0.001
runcurtis_f2( male_exposure_prop=0.2, max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), cex.axis = 0.6, addLegend=FALSE, main='', maxX = 200 )

@@

#freq1 0.001, eff1 0.8
runcurtis_f2( male_exposure_prop=0.2, max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 200 )

>>>>

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('exposure: 0.5', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 120 )

@@

#effectiveness1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 120 )

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('exposure: 0.8', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#exposure 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.8 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), cex.axis = 0.8, addLegend=FALSE, main='', maxX = 120 )

@@

#eff1 & expos 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.8 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 120 )

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1: 0.5', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1: 0.8', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

```{r, eval=TRUE, echo=FALSE, fig.height=7, fig.width=7, fig.show='hold', fig.align='left', fig.cap="Higher effectivenesses for both insecticides, times-to-resistance longer for the mixture in all scenarios. A. Effectiveness of insecticide1 increased from 0.5 to 0.8, B. Effectiveness of insecticide1 increased from 0.5 to 1, C. Effectiveness of insecticides 1 and 2 increased to 0.8, D. Effectiveness of insecticide2 0.8 and of insecticide1 1"}

#4 panel figure looking at effectiveness changes alone

#test of rearranging figures on a grid
#eff1  0.8  1
#eff2
#0.5    1   2
#0.8    3   4

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness2: 0.5', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

#eff1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150 )

#eff1 1 eff2 0.5
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 1 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150 )

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness2: 0.8', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

#eff1 0.8 eff2 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.8 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150 )

#eff1 1 eff2 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 1 , phi.SS2_0B = 0.8 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150 )

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1: 0.8', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1: 1', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('dominance1: 0.5', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#rr1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.8 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 120 )

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('dominance1: 0.8', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#dominance1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.8 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), cex.axis = 0.8, addLegend=FALSE, main='', maxX = 120 )

@@

#dom1 & rr1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.8 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.8 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 120 )

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('resistance restoration1: 0.5', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('resistance restoration1: 0.8', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('frequency1: 1%', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150 )

@@

#eff1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150 )

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('frequency1: 0.1%', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#freq1 0.001
runcurtis_f2( max_gen=500,  P_1 = 0.001 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150 )

@@

#freq1 0.001, eff1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.001 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150 )

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1: 0.5', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1: 0.8', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('male exposure: 0.8', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

runcurtis_f2( male_exposure_prop=0.8, max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 200 )

@@

#eff1 0.8
runcurtis_f2( male_exposure_prop=0.8, max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 200 )

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('male exposure:0.2', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#freq1 0.001
runcurtis_f2( male_exposure_prop=0.2, max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), cex.axis = 0.8, addLegend=FALSE, main='', maxX = 200 )

@@

#freq1 0.001, eff1 0.8
runcurtis_f2( male_exposure_prop=0.2, max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 200 )
